---
title: "Analysis by age and gender, TME/leukapheresis/CSF/CAR product"
author: "heinin"
date: "2024-11-13"
output:
  workflowr::wflow_html:
    code_folding: hide
  html_notebook: default
editor_options:
  chunk_output_type: console
---

## Analysis of cell type proportions and gene expression by age and gender

### Libraries, helper functions, and environment variables

```{r, message = F, warning = F}

library(workflowr)
library(Seurat)
library(googlesheets4)
library(dplyr)
library(tidyverse)
library(ggrepel)
library(patchwork)
library(ggcorrplot)

source("/home/hnatri/GBM_sexdiff/code/CART_plot_functions.R")
source("/home/hnatri/GBM_sexdiff/code/13384_age_sex_themes.R")

setwd("/home/hnatri/GBM_sexdiff/")

set.seed(1234)
options(future.globals.maxSize = 30000 * 1024^2)
reduction <- "integrated_sct_umap"

```

### Import data

```{r, message = F, warning = F, fig.width = 4, fig.height = 3}

immune_fibro <- readRDS("/tgen_labs/banovich/BCTCSF/Heini/13384_Tumor/tumor_immune_fibroblast_reclustered_DoubletFinder.rds")

leukPBMC <- readRDS("/tgen_labs/banovich/BCTCSF/Heini/13384_leukPBMC/CITE_nonCITE_leukPBMC_integrated_merged_AzimuthAnnot.rds")

#CSF <- readRDS("/tgen_labs/banovich/BCTCSF/Heini/13384_CSF_PBMC/13384_csf_integrated_TCR.rds")

object_list <- list("immune_fibro" = immune_fibro,
                    "leukPBMC" = leukPBMC)
                    #"CSF" = CSF)

# Adding demographic info and IDH status
demographics <- read.csv("/home/hnatri/GBM_sexdiff/data/13384_demographic_info.csv",
                         row.names = 1)

gs4_deauth()
idh_info  <- gs4_get("https://docs.google.com/spreadsheets/d/1ApwXjEVtpPB87al6q3ab8TKvZYJTh3iNH1cuO-A_OoU/edit?usp=sharing")
idh_info <- read_sheet(idh_info, sheet = "Clinical info")

object_list <- lapply(object_list, function(xx){
  xx$Gender <- mapvalues(x = xx$UPN,
                         from = demographics$UPN,
                         to = demographics$GENDER)
  xx$Age <- mapvalues(x = xx$UPN,
                      from = demographics$UPN,
                      to = demographics$Age)
  xx$Race <- mapvalues(x = xx$UPN,
                       from = demographics$UPN,
                       to = demographics$RACE_STD)
  xx$Ethnicity <- mapvalues(x = xx$UPN,
                            from = demographics$UPN,
                            to = demographics$ETHNICITY_STD)
  xx@meta.data$IDH <- mapvalues(xx$UPN,
                                from = idh_info$UPN,
                                to = idh_info$idh_mutated) %>%
  unlist() %>%
  as.numeric()
  
  xx@meta.data$IDH[-which(xx@meta.data$UPN %in% idh_info$UPN)] <- NA
  xx$IDH <- gsub(0, "N", xx$IDH)
  xx$IDH <- gsub(1, "Y", xx$IDH)
  
  xx
})

# No demographic info for 208?
object_list[["leukPBMC"]] <- subset(object_list[["leukPBMC"]], subset = UPN %in% c(208), invert = T)

# Numbers of samples by group
n_samples <- object_list[["immune_fibro"]]@meta.data %>%
  dplyr::select(UPN, Gender, CD3_high_low, binary_response, IDH) %>%
  distinct()

table(n_samples$Gender)
table(n_samples$Gender, n_samples$IDH)
table(n_samples$Gender, n_samples$binary_response)
table(n_samples$IDH, n_samples$binary_response)

```

## TME (immune cells + fibroblasts)

### Cell type proportions by age

```{r, message = F, warning = F, fig.width = 6, fig.height = 3}

# Linear regression by celltype, not stratifying by gender
prop_table <- as.data.frame(table(as.character(object_list[["immune_fibro"]]$UPN), object_list[["immune_fibro"]]$celltype))
colnames(prop_table) <- c("UPN", "celltype", "Freq")
prop_table <- spread(prop_table, celltype, Freq)
prop_table[,2:length(prop_table)] <- (prop_table[,2:length(prop_table)]/rowSums(prop_table[,2:length(prop_table)]))*100
prop_table <- gather(prop_table, celltype, Freq, names(prop_table)[2:length(names(prop_table))], factor_key=TRUE)
prop_table$Age  <- mapvalues(x = prop_table$UPN,
                             from = demographics$UPN,
                             to = demographics$Age)
prop_table$Age <- as.numeric(as.character(prop_table$Age))
prop_table$Gender  <- mapvalues(x = prop_table$UPN,
                                from = demographics$UPN,
                                to = demographics$GENDER)

ct_prop_res <- as.data.frame(matrix(NA, nrow = length(unique(prop_table$celltype)),
                                    ncol = 3))
colnames(ct_prop_res) <- c("celltype", "R2", "p")
ct_prop_res$celltype <- sort(unique(prop_table$celltype))

for(ct in unique(ct_prop_res$celltype)){
    data_subset <- prop_table %>% filter(celltype == ct)
    #if(nrow(data_subset)<2){
    #  next
    #} else {
    lm_res <- lm(Freq~Age, data = data_subset)
    pval <- summary(lm_res)$coefficients[,4][2]
    r2 <- summary(lm_res)$r.squared
    
    ct_prop_res[which(ct_prop_res$celltype == ct),]$R2 <- r2
    ct_prop_res[which(ct_prop_res$celltype == ct),]$p <- as.numeric(pval)
}

ct_prop_res

ct_prop_res %>% dplyr::select(c("celltype", "R2")) %>%
  ggplot(aes(x = celltype, y = R2, fill = celltype)) +
    geom_bar(stat="identity", position='stack', width = 0.8) +
    scale_fill_manual(name = "celltype", values = immune_fibro_celltype_col) + 
    theme_bw() +
    xlab("Cell type") + 
    ylab("R2 of celltype abundance by age") +
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm"))

```

Plotting cell type proportions by age

```{r, message = F, warning = F, fig.width = 12, fig.height = 12}

prop_table %>%
  ggplot(aes(x = Age, y = Freq, color = celltype)) +
    geom_point() +
    scale_color_manual(name = "celltype", values = immune_fibro_celltype_col) + 
    theme_bw() +
    xlab("Age") + 
    ylab("Cell type abundance") + 
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm")) +
    geom_smooth(method = "lm", se = T, formula = y ~ x) +
    facet_wrap(~celltype, scales = "free")

```

### Cell type proportions by gender and age

```{r, message = F, warning = F, fig.width = 5, fig.height = 5}

# Linear regression by celltype
ct_prop_res_gender <- as.data.frame(matrix(NA, nrow = 2*length(unique(prop_table$celltype)),
                                    ncol = 4))
colnames(ct_prop_res_gender) <- c("gender", "celltype", "R2", "p")
ct_prop_res_gender$celltype <- rep(sort(unique(prop_table$celltype)), 2)
ct_prop_res_gender$gender <- c(rep(c("Male"), length(unique(prop_table$celltype))),
                               rep(c("Female"), length(unique(prop_table$celltype))))


for(ct in unique(ct_prop_res_gender$celltype)){
  for(gender in c("Male", "Female")){
    data_subset <- prop_table %>% filter(celltype == ct,
                                         Gender == gender)
    #if(nrow(data_subset)<2){
    #  next
    #} else {
    lm_res <- lm(Freq~Age, data = data_subset)
    pval <- summary(lm_res)$coefficients[,4][2]
    r2 <- summary(lm_res)$r.squared
    
    ct_prop_res_gender[which(ct_prop_res_gender$celltype == ct & ct_prop_res_gender$gender == gender),]$R2 <- r2
    ct_prop_res_gender[which(ct_prop_res_gender$celltype == ct & ct_prop_res_gender$gender == gender),]$p <- as.numeric(pval)
    }
}

ct_prop_res_gender

ct_prop_res_gender %>% dplyr::select(c("celltype", "R2", "gender")) %>%
  pivot_wider(values_from = "R2", names_from = "gender") %>%
  ggplot(aes(x = Male, y = Female, color = celltype, label = celltype)) +
    geom_point() +
    scale_color_manual(name = "celltype", values = immune_fibro_celltype_col) + 
    theme_bw() +
    xlab("R2 of cell type abundance correlation with with age, male") + 
    ylab("R2 of cell type abundance correlation with with age, female") + 
    geom_text_repel(size = 2.5) +
    theme(legend.position = "none") + 
    geom_abline(intercept = 0, slope = 1, linewidth = 0.5, linetype = "dashed") +
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm"))

```

```{r, message = F, warning = F, fig.width = 12, fig.height = 4}

ct_prop_res_gender %>% dplyr::select(c("celltype", "R2", "gender")) %>%
  ggplot(aes(x = celltype, y = R2, fill = celltype)) +
    geom_bar(stat="identity", position='stack', width = 0.8) +
    scale_fill_manual(name = "celltype", values = immune_fibro_celltype_col) + 
    theme_bw() +
    xlab("Cell type") + 
    ylab("R2 of celltype abundance by age") +
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm")) +
    facet_wrap(~gender, scales = "fixed")

```

Plotting cell type proportions by age and gender

```{r, message = F, warning = F, fig.width = 20, fig.height = 25}

prop_table %>%
  ggplot(aes(x = Age, y = Freq, color = celltype)) +
    geom_point() +
    scale_color_manual(name = "celltype", values = immune_fibro_celltype_col) + 
    theme_bw() +
    xlab("Age") + 
    ylab("Cell type abundance") + 
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm")) +
    geom_smooth(method = "lm", se = T, formula = y ~ x) +
    facet_wrap(~celltype+Gender, scales = "free", ncol = 6)

```

### Multiple variate regression by age and gender

```{r, message = F, warning = F, fig.width = 10, fig.height = 10}

prop_table$Gender_num <- ifelse(prop_table$Gender == "Male", 1,
                                ifelse(prop_table$Gender == "Female", 0, NA))

ct_prop_res_multivar <- as.data.frame(matrix(NA, nrow = length(unique(prop_table$celltype)),
                                    ncol = 5))
colnames(ct_prop_res_multivar) <- c("celltype", "R2", "pval_intercept", "pval_age", "pval_gender")
ct_prop_res_multivar$celltype <- sort(unique(prop_table$celltype))

for(ct in unique(ct_prop_res_multivar$celltype)){
    data_subset <- prop_table %>% filter(celltype == ct)
    #if(nrow(data_subset)<2){
    #  next
    #} else {
    lm_res <- lm(Freq ~ Age + Gender_num, data = data_subset)
    pval_intercept <- summary(lm_res)$coefficients[,4][1]
    pval_age <- summary(lm_res)$coefficients[,4][2]
    pval_gender <- summary(lm_res)$coefficients[,4][3]
    r2 <- summary(lm_res)$r.squared
    
    ct_prop_res_multivar[which(ct_prop_res_multivar$celltype == ct),]$R2 <- r2
    ct_prop_res_multivar[which(ct_prop_res_multivar$celltype == ct),]$pval_intercept <- as.numeric(pval_intercept)
    ct_prop_res_multivar[which(ct_prop_res_multivar$celltype == ct),]$pval_age <- as.numeric(pval_age)
    ct_prop_res_multivar[which(ct_prop_res_multivar$celltype == ct),]$pval_gender <- as.numeric(pval_gender)
}

ct_prop_res_multivar %>%
  arrange(pval_intercept)# %>% filter(pval_intercept < 0.1)

# Data for a correlation plot
prop_table_corr <- prop_table %>%
  pivot_wider(names_from = celltype, values_from = Freq) %>%
  dplyr::select(-c("UPN", "Gender"))

# Compute correlation at 2 decimal places
corr_matrix <- round(cor(prop_table_corr), 2)

# Plot
ggcorrplot(corr_matrix, hc.order = TRUE, type = "lower",
          lab = TRUE, lab_size = 3)

```

```{r, message = F, warning = F, fig.width = 10, fig.height = 10}

plot_cts <- ct_prop_res_multivar %>% filter(pval_intercept < 0.1) %>%
  dplyr::select(celltype) %>%
  unlist()

prop_table %>%
  filter(celltype %in% plot_cts) %>%
  ggplot(aes(x = Age, y = Freq, color = celltype)) +
    geom_point() +
    scale_color_manual(name = "celltype", values = immune_fibro_celltype_col) + 
    theme_bw() +
    xlab("Age") + 
    ylab("Cell type abundance") + 
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm")) +
    geom_smooth(method = "lm", se = T, formula = y ~ x) +
    facet_wrap(~celltype+Gender, scales = "free", ncol = 4)

```

## Leukapheresis PBMCs

```{r, message = F, warning = F, fig.width = 6, fig.height = 6}

DimPlot(leukPBMC,
        group.by = "celltype.l1",
        cols = leukPBMC_celltype_1_col,
        reduction = "wnn.umap",
        label = T,
        label.box = T,
        label.size = 3,
        repel = T,
        raster = T,
        raster.dpi = c(1024, 1024),
        pt.size = 3) +
  ggtitle("Cell type") +
  theme_classic() +
  NoLegend() +
  NoAxes() +
  coord_fixed(1)

DimPlot(leukPBMC,
        group.by = "celltype.l2",
        cols = leukPBMC_celltype_2_col,
        reduction = "wnn.umap",
        label = T,
        label.box = T,
        label.size = 3,
        repel = T,
        raster = T,
        raster.dpi = c(1024, 1024),
        pt.size = 3) +
  ggtitle("Cell type") +
  theme_classic() +
  NoLegend() +
  NoAxes() +
  coord_fixed(1)

DimPlot(leukPBMC,
        group.by = "celltype.l3",
        #cols = leukPBMC_celltype_col,
        reduction = "wnn.umap",
        label = T,
        label.box = T,
        label.size = 3,
        repel = T,
        raster = T,
        raster.dpi = c(1024, 1024),
        pt.size = 3) +
  ggtitle("Cell type") +
  theme_classic() +
  NoLegend() +
  NoAxes() +
  coord_fixed(1)

```

Cell numbers by cell type

```{r, message = F, warning = F, fig.width = 6, fig.height = 4}

table(leukPBMC$celltype.l2) %>%
  as.data.frame() %>%
  ggplot(aes(x = reorder(Var1, -Freq), y = Freq)) + 
  geom_bar(stat = "identity") +
  theme_minimal() +
  RotatedAxis() +
  xlab("Cell type (l2)") +
  ylab("# cells")

```

Only analyzing cell types with >10 samples with >10 cells

```{r, message = F, warning = F, fig.width = 6, fig.height = 4}


```

### Cell type proportions by age

```{r, message = F, warning = F, fig.width = 6, fig.height = 4}

# Linear regression by celltype, not stratifying by gender
prop_table <- as.data.frame(table(as.character(object_list[["leukPBMC"]]$UPN), object_list[["leukPBMC"]]$celltype.l2))
colnames(prop_table) <- c("UPN", "celltype", "Freq")
prop_table <- spread(prop_table, celltype, Freq)
prop_table[,2:length(prop_table)] <- (prop_table[,2:length(prop_table)]/rowSums(prop_table[,2:length(prop_table)]))*100
prop_table <- gather(prop_table, celltype, Freq, names(prop_table)[2:length(names(prop_table))], factor_key=TRUE)
prop_table$Age  <- mapvalues(x = prop_table$UPN,
                             from = demographics$UPN,
                             to = demographics$Age)
prop_table$Age <- as.numeric(as.character(prop_table$Age))
prop_table$Gender  <- mapvalues(x = prop_table$UPN,
                                from = demographics$UPN,
                                to = demographics$GENDER)

ct_prop_res <- as.data.frame(matrix(NA, nrow = length(unique(prop_table$celltype)),
                                    ncol = 3))
colnames(ct_prop_res) <- c("celltype", "R2", "p")
ct_prop_res$celltype <- sort(unique(prop_table$celltype))

for(ct in unique(ct_prop_res$celltype)){
    data_subset <- prop_table %>% filter(celltype == ct)
    #if(nrow(data_subset)<2){
    #  next
    #} else {
    lm_res <- lm(Freq~Age, data = data_subset)
    pval <- summary(lm_res)$coefficients[,4][2]
    r2 <- summary(lm_res)$r.squared
    
    ct_prop_res[which(ct_prop_res$celltype == ct),]$R2 <- r2
    ct_prop_res[which(ct_prop_res$celltype == ct),]$p <- as.numeric(pval)
}

ct_prop_res

ct_prop_res %>% dplyr::select(c("celltype", "R2")) %>%
  ggplot(aes(x = celltype, y = R2, fill = celltype)) +
    geom_bar(stat="identity", position='stack', width = 0.8) +
    scale_fill_manual(name = "celltype", values = leukPBMC_celltype_2_col) + 
    theme_bw() +
    xlab("Cell type") + 
    ylab("R2 of celltype abundance by age") +
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm")) +
    RotatedAxis()

```

Plotting cell type proportions by age

```{r, message = F, warning = F, fig.width = 16, fig.height = 12}

prop_table %>%
  ggplot(aes(x = Age, y = Freq, color = celltype)) +
    geom_point() +
    scale_color_manual(name = "celltype", values = leukPBMC_celltype_2_col) + 
    theme_bw() +
    xlab("Age") + 
    ylab("Cell type abundance") + 
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm")) +
    geom_smooth(method = "lm", se = T, formula = y ~ x) +
    facet_wrap(~celltype, scales = "free")

```

### Cell type proportions by gender and age

```{r, message = F, warning = F, fig.width = 5, fig.height = 5}

# Linear regression by celltype
ct_prop_res_gender <- as.data.frame(matrix(NA, nrow = 2*length(unique(prop_table$celltype)),
                                    ncol = 4))
colnames(ct_prop_res_gender) <- c("gender", "celltype", "R2", "p")
ct_prop_res_gender$celltype <- rep(sort(unique(prop_table$celltype)), 2)
ct_prop_res_gender$gender <- c(rep(c("Male"), length(unique(prop_table$celltype))),
                               rep(c("Female"), length(unique(prop_table$celltype))))


for(ct in unique(ct_prop_res_gender$celltype)){
  for(gender in c("Male", "Female")){
    data_subset <- prop_table %>% filter(celltype == ct,
                                         Gender == gender)
    #if(nrow(data_subset)<2){
    #  next
    #} else {
    lm_res <- lm(Freq~Age, data = data_subset)
    pval <- summary(lm_res)$coefficients[,4][2]
    r2 <- summary(lm_res)$r.squared
    
    ct_prop_res_gender[which(ct_prop_res_gender$celltype == ct & ct_prop_res_gender$gender == gender),]$R2 <- r2
    ct_prop_res_gender[which(ct_prop_res_gender$celltype == ct & ct_prop_res_gender$gender == gender),]$p <- as.numeric(pval)
    }
}

ct_prop_res_gender

ct_prop_res_gender %>% dplyr::select(c("celltype", "R2", "gender")) %>%
  pivot_wider(values_from = "R2", names_from = "gender") %>%
  ggplot(aes(x = Male, y = Female, color = celltype, label = celltype)) +
    geom_point() +
    scale_color_manual(name = "celltype", values = leukPBMC_celltype_2_col) + 
    theme_bw() +
    xlab("R2 of cell type abundance correlation with with age, male") + 
    ylab("R2 of cell type abundance correlation with with age, female") + 
    geom_text_repel(size = 2.5) +
    theme(legend.position = "none") + 
    geom_abline(intercept = 0, slope = 1, linewidth = 0.5, linetype = "dashed") +
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm"))

```

```{r, message = F, warning = F, fig.width = 12, fig.height = 4}

ct_prop_res_gender %>% dplyr::select(c("celltype", "R2", "gender")) %>%
  ggplot(aes(x = celltype, y = R2, fill = celltype)) +
    geom_bar(stat="identity", position='stack', width = 0.8) +
    scale_fill_manual(name = "celltype", values = leukPBMC_celltype_2_col) + 
    theme_bw() +
    xlab("Cell type") + 
    ylab("R2 of celltype abundance by age") +
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm")) +
    facet_wrap(~gender, scales = "fixed") +
  RotatedAxis()

```

Plotting cell type proportions by age and gender

```{r, message = F, warning = F, fig.width = 20, fig.height = 28}

prop_table %>%
  ggplot(aes(x = Age, y = Freq, color = celltype)) +
    geom_point() +
    scale_color_manual(name = "celltype", values = leukPBMC_celltype_2_col) + 
    theme_bw() +
    xlab("Age") + 
    ylab("Cell type abundance") + 
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm")) +
    geom_smooth(method = "lm", se = T, formula = y ~ x) +
    facet_wrap(~celltype+Gender, scales = "free", ncol = 6)

```

### Multiple variate regression by age and gender

```{r, message = F, warning = F, fig.width = 10, fig.height = 10}

prop_table$Gender_num <- ifelse(prop_table$Gender == "Male", 1,
                                ifelse(prop_table$Gender == "Female", 0, NA))

ct_prop_res_multivar <- as.data.frame(matrix(NA, nrow = length(unique(prop_table$celltype)),
                                    ncol = 5))
colnames(ct_prop_res_multivar) <- c("celltype", "R2", "pval_intercept", "pval_age", "pval_gender")
ct_prop_res_multivar$celltype <- sort(unique(prop_table$celltype))

for(ct in unique(ct_prop_res_multivar$celltype)){
    data_subset <- prop_table %>% filter(celltype == ct)
    #if(nrow(data_subset)<2){
    #  next
    #} else {
    lm_res <- lm(Freq ~ Age + Gender_num, data = data_subset)
    pval_intercept <- summary(lm_res)$coefficients[,4][1]
    pval_age <- summary(lm_res)$coefficients[,4][2]
    pval_gender <- summary(lm_res)$coefficients[,4][3]
    r2 <- summary(lm_res)$r.squared
    
    ct_prop_res_multivar[which(ct_prop_res_multivar$celltype == ct),]$R2 <- r2
    ct_prop_res_multivar[which(ct_prop_res_multivar$celltype == ct),]$pval_intercept <- as.numeric(pval_intercept)
    ct_prop_res_multivar[which(ct_prop_res_multivar$celltype == ct),]$pval_age <- as.numeric(pval_age)
    ct_prop_res_multivar[which(ct_prop_res_multivar$celltype == ct),]$pval_gender <- as.numeric(pval_gender)
}

ct_prop_res_multivar %>%
  arrange(pval_intercept)# %>% filter(pval_intercept < 0.1)

# Data for a correlation plot
prop_table_corr <- prop_table %>%
  pivot_wider(names_from = celltype, values_from = Freq) %>%
  dplyr::select(-c("UPN", "Gender"))

# Compute correlation at 2 decimal places
corr_matrix <- round(cor(prop_table_corr), 2)

# Plot
#ggcorrplot(corr_matrix, hc.order = TRUE, type = "lower",
#          lab = TRUE, lab_size = 3)

```

```{r, message = F, warning = F, fig.width = 10, fig.height = 20}

plot_cts <- ct_prop_res_multivar %>% filter(pval_intercept < 0.1) %>%
  dplyr::select(celltype) %>%
  unlist()

prop_table %>%
  filter(celltype %in% plot_cts) %>%
  ggplot(aes(x = Age, y = Freq, color = celltype)) +
    geom_point() +
    scale_color_manual(name = "celltype", values = leukPBMC_celltype_2_col) + 
    theme_bw() +
    xlab("Age") + 
    ylab("Cell type abundance") + 
    theme(legend.position = "none") + 
    theme(panel.background = element_rect(colour = "gray88")) +
    theme(plot.margin = margin(0.3, 0.3, 0.3,0.3, "cm")) +
    geom_smooth(method = "lm", se = T, formula = y ~ x) +
    facet_wrap(~celltype+Gender, scales = "free", ncol = 4)

```


## Gene expression correlation by age, gender, and cell type

Pseudobulking by cell type and by compartment (myeloid, lymphoid, fibroblast)

```{r, message = F, warning = F, fig.width = 4, fig.height = 3}

# AverageExpression or AggregateExpression
#ave_exp_mx <- AverageExpression(subset(immune_fibro, subset = cellname %in% keep),
#                                  group.by = c("annot"),
#                                  assay = "RNA",
#                                  layer = "counts",
#                                  normalization.method = "LogNormalize",
#                                  return.seurat = F)
#ave_exp_mx <- as.data.frame(ave_exp_mx$RNA)


```


